Aligning marine species range data to better serve science and conservation

### 2016-03-27 manuscript-main.Rmd
created four maps image
still working on supplemental

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin S. Halpern<sup>1, 2, 3</sup>

output:
  word_document: default
  pdf_document:
    number_sections: yes
    toc: no
  html_document:
    highlight: haddock
    number_sections: yes
    theme: spacelab
    toc: no
---

@@

``` {r SOM, child = 'ms_6_supplemental.Rmd'}
```

>>>>

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern<sup>1, 2, 3</sup>
output:
  word_document: default
  pdf_document:
    number_sections: yes
    toc: no
  html_document:
    highlight: haddock
    number_sections: yes
    theme: spacelab
    toc: no
---

@@

``` {r SOM, child = 'ms_6_supplemental.Rmd', eval = TRUE}
```

### 2016-03-27 ms_6_supplemental.Rmd
created four maps image
still working on supplemental

@@

Oculina varicosa - Ivory tree coral ![oculina_pic.jpg](figures/oculina/oculina_pic.jpg)

@@

plotted against a 200 m bathymetry line: ![oculina_map.png](figures/oculina/oculina_map.png)

>>>>

<!--
![](figures/si_four_maps.png)
-->

a) quad 1: Kajikia albida
b) quad 2: Conus episcopatus
c) quad 3: Conus magnificus
d) quad 4: Acanthurus nigroris

@@

<!--
Oculina varicosa - Ivory tree coral ![oculina_pic.jpg](figures/oculina/oculina_pic.jpg)
-->

@@

plotted against a 200 m bathymetry line:

![oculina varicosa](figures/si_coralmap.png)
